Proposal full title \\ Proposal Acronym

### 2001-10-04 drafts/IST/PartA.tex
foo
svn path=/trunk/; revision=1469

well in the Libre software community than in the software industry. Indeed
they were poorly designed and had evolved quickly to provide functionnalities
to developpers. The resulting platforms suffer from some annoying flaws :

<ul> 
<li> Also due to the number of services and their inter-relations, it is not
	simple to set up a new site that provides hosting. This is a real
	brake to a large number of sites using this technology.
	There is no complete solutions to install easily any of the technologies
	described above.
<li> They are hard to distribute, they were mainly designed as a front end to
	a group of dedicated machines that provide the given set of 
	functionnalities, versionning system, web access, or data base 
	access. Even if the access is remote all data is centralized,
	as one site hosts a huge number of projects. This is a bad
	practice in terms of data safety, data access and scalability.
<li> They rely too much on managing procedures and human control. For example, a site
	needs to be managed by peoplata for mrtg. These script are used on es.gnu.org and france.fsfeurope.org
es that acknowledge project creation.
<li> The most active effort to build such a sytem has recently become proprietary.
Therefore the produced work is not available.
</ul>
\subsection*{Description of the work (max 2000 characters)}
to be written
\subsection*{Milestones and expected result (max 500 characters)}

>>>>

well in the Libre software community than in the software industry. \\
Due to a quick design, they are hard to distribute. They mainly are a front end
to a group of dedicated machines that provides a precise set of
functionnalities. Even if the acces is remote, all data is centralized as one
site physically hosts an huge number of projects. This is bad practice in terms
of data safety, data access and scalability. \\
Also due to the number of services and their inter-relations, it is not simple
to set up a new site that provides hosting. This is a real brake to a large
number of sites using this technology.  There is no complete solutions to
install easily any of the technologies described above. \\
They rely too much on managing procedures and human control. For example, a
site needs to be managed by people that acknowledge project creation. \\
At last the most active effort to build such a sytem has recently become
proprietary.  Therefore the produced work is not available. 
\subsection*{Description of the work (max 2000 characters)} to be written
\subsection*{Milestones and expected result (max 500 characters)}
